Temporal Graph Cube

### 2023-01-29 revision/response.tex

\item test

\end{itemize}

The point-to-point responses are given below.

\section{Response to Reviewer \#1}
\begin{Comments}
The expression of motivation is not clearly. Does the limitation of static graph cube is it cannot support range queries or it only can support latest data?
\end{Comments}
\noindent \textbf{Response:} [todo]. The major limitation of static graph cube is that it cannot support temporal multidimensional networks. Static graph cube can only be built on static multidimensional networks, e.g., DBLP where temporal information of co-authorships is omitted. Consequently, static graph cube cannot support range queries since there is no temporal information in its dataset. Static graph cube cannot support latest data because its authors didn't consider that new edges may be added into the static networks. Temporal graph cube supports latest data because we will update the temporal networks and indexes when new edges are added.

@@

\begin{Comments}
Authors should improve their writing. Especially the punctuation makes the definitions hard to be understood.
\end{Comments}
\noindent \textbf{Response:} test

\begin{Comments}
Authors provide similarity of snapshots and two ratios in the Sec. 5. All of them are calculated based on the edges’ number. Why do you use similarity but not two ratios to proof the effectiveness?
\end{Comments}
\noindent \textbf{Response:} Actually we do use the two ratios to proof the effectiveness of the index. As in our experiments (see Table 6 of Section 7.3), we show the two ratios in the 5-th and 8-th column to proof the actual effectiveness of the index. Similarity of snapshots is the metric which has a strong correlation with the two ratios, so it is used to measure the necessity of building index for a materialized view. In detail, both theoretically and experimentally we find that larger similarity of snapshots in a materialized view leads to higher acceleration ratio and lower space consumption ratio of the index. If the value of similarity of snapshots in a view is as low as $ 1 $, then there is no need to build index for the view and the baseline method to conduct queries is the best method, as we analyzed in Section 5.
%Acceleration ratio in Definition 7 and space consumption ratio in Definition 9 theoretically measure the query efficiency and space cost of the index respectively based on the edges' number. As in our experiments (see Table 6 of Section 7.3), we show the two ratios in the 5-th and 8-th column to proof the actual effectiveness of the index. However, both theoretically and experimentally we find that the query efficiency and space cost of the index are both related to a metric named 'similarity of snapshots' in the manuscript, as shown in Table 6. If the value of similarity of snapshot. To sum up, we do use the two ratios to proof the effectiveness of the index, and similarity of snapshots is used to

\begin{Comments}
In the experiments, authors should add an experiment of comparison with existing methods to evaluate the efficiency of their model.
\end{Comments}
\noindent \textbf{Response:} Following your advice, we have added experiments of existing methods in Section 7.2 and Exp-1 of Section 7.3 to evaluate the effectiveness and efficiency of our model. First, in Section 7.2 we add experimental results of queries in static graph cube. By comparing the query results we show that queries in temporal graph cube can reveal hidden information which may be ignored using queries in static graph cube. Second, at the end of Exp-1 of Section 7.3 we implement two other kinds of indexes, prefix array and sparse table, to accelerate range queries of temporal graph cube. These two indexes both can achieve $ O(1) $ time complexity in conducting range queries on normal numeric arrays. However, in the case of snapshot arrays, only sparse table achieves higher acceleration ratio, but with unacceptable space consumption ratio (sometimes out of memory). Overall, segment-tree based method in manuscript is the most suitable method to accelerate range queries in temporal graph cube.

\begin{Comments}
The study of related works is insufficient, and some of the results and limitations of existing works are not discussed.
\end{Comments}
\noindent \textbf{Response:} Thanks for pointing out this problem. We have reviewed more works mainly related to graph OLAP and graph stream summarization in Section 8 of the revised version, and we have added discussion about limitations of all the mentioned existing works.

@@

\begin{Comments}
The second parameter of MergeSnapshotExtre on Line 11, Algorithm 5 should be (u’, v’, t, a)?
\end{Comments}
\noindent \textbf{Response:} The parameter should remain $ (u',v',a,a) $. In line 11 of Algorithm 5, the algorithm inserts $ e' $ into $ treeNode.snapshot $, which is equivalent to merge two snapshots: $ treeNode.snapshot $ and a temporary snapshot consisting of only $ e' $. However, edges in snapshot of each tree node are in form of $ (u,v,max,min) $, so we need to transform $ e' $ into $ (u',v',a,a) $, since $ a $ is both the maximum and minimum value of the numeric attribute in $ e' $. $ t $ is only used to determine whether the left child or the right child of $ treeNode $ should also be updated.

\section{Response to Reviewer \#2}
\setcounter{Comments}{0}
\begin{Comments}
D1: The management of snapshots should be described with more details. According to Def. 2, the snapshot is defined with a single timestamps. It looks like that when an edge forms at timestamp t, it never disappears. How do we maintain an edge with time range from t1 to t2? Otherwise, the limitation or applicability of the proposed method should be discussed.
\end{Comments}
\noindent \textbf{Response:} It is reasonable for a temporal edge to have only one timestamp, because in many cases, durations or end time of temporal edges are meaningless. For example, DBLP only records date of publication of research papers. For a research paper, the end time of publication or existence is meaningless. We just need to focus on the fact that at a certain time, some researchers have published a certain paper. Given a time range $ [t_1,t_2] $, it's easy to determine whether a research paper is published in $ [t_1,t_2] $. It's the same with movies in IMDB. Another example is email communication network, which is also temporal network. Temporal edges in email communication network contain only timestamp of sending the email, and there is no need to store timestamp of finishing sending the email or timestamp of deleting the email. We just need to focus on the fact that there was an email exchange between certain people at a certain time, or we can consider this as an instant activity.

The temporal edges you mentioned do exist in temporal networks, such as phone calls network, since each phone call lasts for a while. However,

### 2023-01-30 TemporalGraphCube/TemporalGraphCube_revision.tex
response 1-30
response 1-31

\begin{definition}[Temporal Aggregate Network]
	\label{def:temp_aggregate_network}
	Given a temporal multidimensional network $\Gr=(\Vr,\Sr,A,W)$ and an aggregation $A'=(A'_1,A'_2,...,A'_n)$ where $A'_i$ equals $A_i$ or $\ast$, the obtained temporal aggregate network is another temporal multidimensional network $\Gr'=(\Vr',\Sr',B,W_{\Gr'})$ where $\Vr' \subseteq \Vr$, $B=\{A'_i|A'_i \neq \ast\}$ and
	\begin{enumerate}
		\item \revision{Let $ [v] $ be an equivalence class of $ v $, where $ v \in \Vr $ and $[v]=\{u|B(u)=B(v),u \in \Vr\}$. For each $ v\in \Vr $, $ \exists v' \in \Vr'$ satisfying $v' \in [v]$ and $\nexists u' \in \Vr', u' \neq v'$ satisfying $u' \in [v]$.} $W_{\Gr'}(v')$ is the aggregation result of $W(v)$ for $v \in [v']$ obtained by aggregation function upon vertices specified by user.
%		\item For any $S'_i$ in $\Sr'$ and each $(u',v',a')$ in $S'_i$, there exists a nonempty maximum edge set $E=\{(u,v,a)|(u,v,a) \in S_i, u \in [u'] \wedge v \in [v']\; or\; u \in [v'] \wedge v \in [u']\}$, $a'$ is the aggregation result of numeric attributes ($a$) of edges in $E$ obtained by aggregation function specified by user.
		\item $\forall u',v' \in \Vr'$ where $u' \leq v'$ and any $\Sr[i], i \in [1,t_{end}]$, if there exists a nonempty maximum edge set $E=\{(u,v,a)|(u,v,a) \in \Sr[i],(u \in [u'] \wedge v \in [v']) \vee (u \in [v'] \wedge v \in [u']) \}$, then $ \exists (u',v',a') \in \Sr'[i] $, where $a'$ is the aggregation result of numeric attributes of edges in $E$ obtained by aggregation function upon edges specified by user.
	\end{enumerate}
\end{definition}
In short, conducting aggregations on temp-multi-network contains two stages: aggregating, or group-by on the vertex table as 1) in Definition~\ref{def:temp_aggregate_network} and aggregating each snapshots in the temp-multi-network as 2) in Definition~\ref{def:temp_aggregate_network}.

@@

Before analyzing the time and space complexity of Algorithm~\ref{alg:temp_cuboid_baseline}, we first give a brief definition of summarized snapshot.
\begin{definition}[Summarized Snapshot]
	\label{def:sum_snap}
	Given a temporal multidimensional network $\Gr=(\Vr,\Sr,A,W)$, the summarized snapshot $ S $ of $ \Gr $ is a special snapshot of $ \Gr $, which is the network structure in the result of a temporal cuboid query $ Q=(A,[1+t_{base},t_{end}+t_{base}]) $ on $ \Gr $.
\end{definition}
In other words, summarized snapshot $ S $ of $ \Gr $ can be obtained by merging all snapshots in a snapshot array $ \Sr $.

@@

We can conduct a temporal crossboid query directly on the original temp-multi-network. However, it is inefficient due to the large size of the original temp-multi-network. We omit the algorithm to conduct a temporal crossboid query on the original temp-multi-network, but give a more efficient way to conduct the query.
\begin{definition}[Nearest Common Descendant]
	\label{def:ncd}
	Given two different views $ A_1' $ and $ A_2' $, the common descendant of $ A_1' $ and $ A_2' $, $ cd(A_1',A_2') $ is also a view in temporal graph cube, satisfying $ dim(A_1') \cup dim(A_2') \subseteq dim(cd(A_1',A_2')) $. The nearest common descendant of $ A_1' $ and $ A_2' $, $ ncd(A_1',A_2') $, is one of the common descendants satisfying $ dim(ncd(A_1',A_2'))=dim(A_1') \cup dim(A_2') $.
\end{definition}
\begin{theorem}
	\label{thm:ans_cross_by_ncd}
	Given a temporal crossboid query $ Q_{cross}=(A_1',A_2',[l,r]) $, $ Q_{cross} $ can be answered from the result of the temporal cuboid query $ Q=(ncd(A_1',A_2'),[l,r]) $ where $ Q,Q_{cross} $ share the same aggregation function upon vertices and edges.
\end{theorem}
\comment{
\begin{proof}
	Although the result of $ Q_{cross} $ is a bipartite network, we can treat the edges in it as directed edges and treat each edge in materialized views of the temporal graph cube and in the result of $ Q $ as two directed edges, so that we can use the similar idea from the previous proofs of Theorem~\ref{thm:cuboid_by_temp_aggre_network} and Theorem~\ref{thm:cuboid_by_small_temp_aggre_network} to prove this theorem. We omit the details of this proof due to the space limitation.
\end{proof}
}
%With Theorem~\ref{thm:ans_cross_by_ncd}, a temporal crossboid query can be turned into a temporal cuboid query and we have discussed how to conduct a temporal cuboid query efficiently in \stitle{Temporal cuboid} section.
With Theorem~\ref{thm:ans_cross_by_ncd}, a temporal crossboid query can be turned into a temporal cuboid query, and thus can be solved by our previous techniques.

@@

Consider the second example in Fig.~\ref{fig:index_fail_success_example} (b), all snapshots share the same edges. In this case, if we still merge snapshots in $ [t_1,t_4] $, each edge will be visited $ 4 $ times in the baseline method, therefore it is necessary to build index. Next, we describe the measurement of the necessity of index and the key factor we found which affects the necessity of index.
\begin{definition}[Acceleration Ratio of Index]
	\label{def:acceleration_ratio_index}
	For an array $ Arr $ with numeric values or snapshots, we build a segment tree index on it. For a query $ q=(func,[l,r]) $, assume that the basic components are visited $ C_b $ times using the baseline method and $ C_i $ times using the index-based method, the acceleration ratio of the index on $ q $ is $ \frac{C_b}{C_i} $.
\end{definition}
The basic components in snapshot array and index built on snapshot array are edges. We use the number of visited edges as the measure of time consumption when conducting a query using the baseline method and using the index-based method in Definition~\ref{def:acceleration_ratio_index}.
\begin{definition}[Similarity of Snapshots]
	\label{def:similarity_snapshots}
	Given a snapshot array $ snapArr $ starting from $ 1 $ and containing $ n $ snapshots, the summarized snapshot $ S $ of all snapshots in $ snapArr $, $ E=\sum_{i=1}^{n}|snapArr[i]| $, the similarity of snapshots in $ snapArr $ is $ s=\frac{E}{|S|} $.
\end{definition}
In other words, the similarity of snapshots is the ratio of the total number of edges in snapshot array to the size of the summarized snapshot. For simplicity, we assume that each snapshot in $ snapArr $ has at least one edge. Clearly, for a snapshot array of length $ n $, similarity of snapshots $ s $ is in $ [1,n] $.
\begin{example}
	Consider examples in Fig.~\ref{fig:similarity}.
	\begin{figure}[t] %\vspace*{-0.5cm}
		\begin{center}
			\begin{tabular}[t]{c}\hspace*{-0.3cm}
				\subfigure[{\scriptsize $ s=1 $}]{
					\includegraphics[width=0.5\columnwidth]{fig/example/example_similarity_a.pdf}
				}
				\hspace*{-0.5cm}
				\subfigure[{\scriptsize $ s=4 $}]{
					\includegraphics[width=0.5\columnwidth]{fig/example/example_similarity_b.pdf}
				}
				\\
				\subfigure[{\scriptsize $ s=\frac{5}{3} $}]{
					\includegraphics[width=0.5\columnwidth]{fig/example/example_similarity_c.pdf}
				}
				\hspace*{-0.5cm}
				\subfigure[{\scriptsize $ s=4 $}]{
					\includegraphics[width=0.5\columnwidth]{fig/example/example_similarity_d.pdf}
				}
			\end{tabular}
			\vspace*{-0.5cm}
			\caption{Four snapshot arrays with different similarity of snapshots}
			\vspace*{-0.8cm}
			\label{fig:similarity}
		\end{center}
	\end{figure}
	There are 4 snapshot arrays having the same length of 4 but different similarities of snapshots $ s $. In Fig.~\ref{fig:similarity} (a), $ s=1 $, and we can see that there is no edge shared by any two snapshots, or, snapshots in Fig.~\ref{fig:similarity} (a) are not similar to each other. In Fig.~\ref{fig:similarity} (b) and (d), $ s=4 $, all snapshots share the same edges. In Fig.~\ref{fig:similarity} (c), $ s=\frac{5}{3} $, and there are edges shared by some snapshots.
\end{example}
From the above examples, we can see that with the similarity of snapshots grows, there will be more snapshots in snapshot array which are similar to each other, or, more edges are shared by snapshots.

@@

\begin{definition}[Space Consumption Ratio]
	\label{def:space_consum_ratio}
	Consider an array $ Arr $ holding numeric values or snapshots. If $ Arr $ is a snapshot array, suppose the total number of edges in $ Arr $ is $ E_a $, and the total number of edges in the index is $ E_i $. If $ Arr $ is a numeric array, $ E_a,E_i $ are the total number of numeric values in $ Arr $ and in the index respectively. The space consumption ratio of the index is $ \frac{E_i}{E_a} $.
\end{definition}
\begin{theorem}\label{thm:best_index_space_ratio}
	For two arrays of length $ n $ and starting from 1, snapshot array $ snapArr $ and numeric array $ numArr $, if similarity of snapshots in $ snapArr $ equals $ n $, then the space consumption ratios of the same index built on the two arrays are equal.
\end{theorem}
\comment{
\begin{proof}
	We mentioned that in proof of Theorem~\ref{thm:best_index_efficiency}, the structures of STree built on $ numArr $ and $ snapArr $ are the same. It is the same with the array structure of prefix array and STable. We can turn indexes into sets holding elements like: $ (SumElement,[l,r]) $, and if an index is built on $ numArr $, $ SumElement $ is the aggregation result of numeric values in $ [l,r] $, otherwise the summarized snapshot of snapshots in $ [l,r] $. For each index, suppose we build the index on $ numArr $ and $ snapArr $, named $ numIndex $ and $ snapIndex $. There must be a bijection between elements in $ numIndex $ and $ snapIndex $ that for each $ i $ in $ numIndex $, there is a corresponding $ j $ in $ snapIndex $ that $ i $ and $ j $ have the same time range $ [l,r] $, since the structures of $ numIndex $ and $ snapIndex $ are the same. It is easy to know that the space consumption ratio of $ numIndex $ is $ \frac{|numIndex|}{n} $. Since the similarity of snapshots in $ snapArr $ is $ n $, all snapshots in $ snapArr $ and $ snapIndex $ share the same edges. Suppose the summarized snapshot of snapshots in $ snapArr $ is $ S $, the space consumption ratio of $ snapIndex $ is $ \frac{|snapIndex||S|}{n|S|} $, since $ |snapIndex|=|numIndex| $, so the space consumption ratio of $ snapIndex $ and $ numIndex $ are equal.
\end{proof}
}

@@

\begin{table}[t!]%\vspace*{-0.3cm}
	\scriptsize
	%\small
	\centering
	\caption{\revision{Performance of prefix array and sparse table}} \vspace*{-0.2cm} \label{tab:effi_other_index}
	\begin{tabular}{c c c c c c}
		\toprule
		\makecell[c]{View\\No.}& $ s $ &\makecell[c]{acce-ratio\\preArr} &\makecell[c]{Space ratio\\preArr}&\makecell[c]{acce-ratio\\STable}&\makecell[c]{Space ratio\\STable}\cr %\hline %\hline
		\midrule
		1&53.48&5.37 & 1.51 &12.92 &9.38 \cr
		\midrule
		2&18.16&3.20 & 2.58 &7.87 &14.45 \cr
		\midrule
		3&6.15 &1.76 & 5.76 &5.15 &26.78 \cr
		\midrule
		4&6.07 &1.74 & 5.84 &5.15 &27.04 \cr
		\midrule
		5&4.70 &1.56 & 7.14 &4.84 &31.74 \cr
		\midrule
		6&3.97 &1.45 & 8.33 &4.58 &35.85 \cr
		\midrule
		7&1.12 &0.85 &27.38 &OM & OM \cr
		\bottomrule
	\end{tabular}
	\vspace*{-0.4cm}
\end{table}
\revision{We also implement prefix array (preArr, only supports $ f_e= $ SUM($\ast$)) and sparse table (STable, only supports $ f_e= $ MAX($\ast$) or MIN($\ast$)) to conduct the same queries as a comparison. The results are shown in Table~\ref{tab:effi_other_index}. We can see that the acceleration ratio of prefix array is close to our solution (STree) but with more space consumption in most cases. The performance of prefix array is also influenced by similarity of snapshots, as we analyzed in Section~\ref{sec:effec_of_indexes}. The acceleration ratio of sparse table is much higher than that of prefix array and STree, but consumes much more space. Building sparse table even leads to an out-of-memory on the No. 7 view. Similarly, the performance of sparse table is also influenced by similarity of snapshots. Overall, our index-based method, STree, is the best in these three method considering both acceleration ratio and space consumption ratio.}

>>>>

\begin{definition}[Temporal Aggregate Network]
	\label{def:temp_aggregate_network}
	Given a temporal multidimensional network $\Gr=(\Vr,\Sr,A,W)$ and an aggregation $A'=(A'_1,A'_2,...,A'_n)$ where $A'_i$ equals $A_i$ or $\ast$, the obtained temporal aggregate network is another temporal multidimensional network $\Gr'=(\Vr',\Sr',B,W_{\Gr'})$ where $\Vr' \subseteq \Vr$, $B=\{A'_i|A'_i \neq \ast\}$ and
	\begin{enumerate}
		\item \revision{Let $ [v] $ be an equivalence class of $ v $, where $ v \in \Vr $ and $[v]=\{u|B(u)=B(v),u \in \Vr\}$. For each $ v\in \Vr $, $ \exists v' \in \Vr'$ satisfying $v' \in [v]$ and $\nexists u' \in \Vr', u' \neq v'$ satisfying $u' \in [v]$.} $W_{\Gr'}(v')$ is the aggregation result of $W(v)$ for $v \in [v']$ obtained by aggregation function upon vertices specified by user.
%		\item For any $S'_i$ in $\Sr'$ and each $(u',v',a')$ in $S'_i$, there exists a nonempty maximum edge set $E=\{(u,v,a)|(u,v,a) \in S_i, u \in [u'] \wedge v \in [v']\; or\; u \in [v'] \wedge v \in [u']\}$, $a'$ is the aggregation result of numeric attributes ($a$) of edges in $E$ obtained by aggregation function specified by user.
		\item $\forall u',v' \in \Vr'$ where $u' \leq v'$ and \revision{any $\Sr[i]$ for $ i \in [1,t_{end}]$}, if there exists a nonempty maximum edge set $E=\{(u,v,a)|(u,v,a) \in \Sr[i],(u \in [u'] \wedge v \in [v']) \vee (u \in [v'] \wedge v \in [u']) \}$, then $ \exists (u',v',a') \in \Sr'[i] $ where $a'$ is the aggregation result of numeric attributes of edges in $E$ obtained by aggregation function upon edges specified by user.
	\end{enumerate}
\end{definition}
In short, conducting aggregations on temp-multi-network contains two stages: aggregating, or group-by on the vertex table as 1) in Definition~\ref{def:temp_aggregate_network} and aggregating each snapshots in the temp-multi-network as 2) in Definition~\ref{def:temp_aggregate_network}.

@@

Before analyzing the time and space complexity of Algorithm~\ref{alg:temp_cuboid_baseline}, we first give a brief definition of summarized snapshot.
\begin{definition}[Summarized Snapshot]
	\label{def:sum_snap}
	Given a temporal multidimensional network $\Gr=(\Vr,\Sr,A,W)$, the summarized snapshot $ S $ of $ \Gr $ is a special snapshot of $ \Gr $ \revision{and it is the network structure in the result of a temporal cuboid query $ Q=(A,[1+t_{base},t_{end}+t_{base}]) $ on $ \Gr $}.
\end{definition}
In other words, summarized snapshot $ S $ of $ \Gr $ can be obtained by merging all snapshots in a snapshot array $ \Sr $.

@@

We can conduct a temporal crossboid query directly on the original temp-multi-network. However, it is inefficient due to the large size of the original temp-multi-network. We omit the algorithm to conduct a temporal crossboid query on the original temp-multi-network, but give a more efficient way to conduct the query.
\begin{definition}[Nearest Common Descendant]
	\label{def:ncd}
	Given two different views $ A_1' $ and $ A_2' $, \revision{$ cd(A_1',A_2') $ is common descendant of $ A_1' $ and $ A_2' $ and it is also a view in temporal graph cube satisfying $ dim(A_1') \cup dim(A_2') \subseteq dim(cd(A_1',A_2')) $. $ ncd(A_1',A_2') $ is the nearest common descendant of $ A_1' $ and $ A_2' $ and it is one of the common descendants satisfying $ dim(ncd(A_1',A_2'))=dim(A_1') \cup dim(A_2') $.}
\end{definition}
\begin{theorem}
	\label{thm:ans_cross_by_ncd}
	Given a temporal crossboid query $ Q_{cross}=(A_1',A_2',[l,r]) $, $ Q_{cross} $ can be answered from the result of the temporal cuboid query $ Q=(ncd(A_1',A_2'),[l,r]) $ where $ Q,Q_{cross} $ share the same aggregation function upon vertices and edges.
\end{theorem}
\comment{
\begin{proof}
	Although the result of $ Q_{cross} $ is a bipartite network, we can treat the edges in it as directed edges and treat each edge in materialized views of the temporal graph cube and in the result of $ Q $ as two directed edges, so that we can use the similar idea from the previous proofs of Theorem~\ref{thm:cuboid_by_temp_aggre_network} and Theorem~\ref{thm:cuboid_by_small_temp_aggre_network} to prove this theorem. We omit the details of this proof due to the space limitation.
\end{proof}
}
%With Theorem~\ref{thm:ans_cross_by_ncd}, a temporal crossboid query can be turned into a temporal cuboid query and we have discussed how to conduct a temporal cuboid query efficiently in \stitle{Temporal cuboid} section.
With Theorem~\ref{thm:ans_cross_by_ncd}, a temporal crossboid query can be turned into a temporal cuboid query, and thus can be solved by our previous techniques.

@@

Consider the second example in Fig.~\ref{fig:index_fail_success_example} (b), all snapshots share the same edges. In this case, if we still merge snapshots in $ [t_1,t_4] $, each edge will be visited $ 4 $ times in the baseline method, therefore it is necessary to build index. Next, we describe the measurement of the necessity of index and the key factor we found which affects the necessity of index.
\begin{definition}[Acceleration Ratio of Index]
	\label{def:acceleration_ratio_index}
	For an array $ Arr $ with numeric values or snapshots, we build a segment tree index on it. For a query $ q=(func,[l,r]) $, assume that the basic components are visited $ C_b $ times using the baseline method and $ C_i $ times using the index-based method, the acceleration ratio of the index on $ q $ is $ \frac{C_b}{C_i} $.
\end{definition}
The basic components in snapshot array and index built on snapshot array are edges. We use the number of visited edges as the measure of time consumption when conducting a query using the baseline method and using the index-based method in Definition~\ref{def:acceleration_ratio_index}.
\begin{definition}[Similarity of Snapshots]
	\label{def:similarity_snapshots}
	Given a snapshot array $ snapArr $ starting from $ 1 $ and containing $ n $ snapshots. \revision{Suppose the summarized snapshot of all snapshots in $ snapArr $ is $ S $ and $ E=\sum_{i=1}^{n}|snapArr[i]| $}, the similarity of snapshots in $ snapArr $ is $ s=\frac{E}{|S|} $.
\end{definition}
In other words, the similarity of snapshots is the ratio of the total number of edges in snapshot array to the size of the summarized snapshot. For simplicity, we assume that each snapshot in $ snapArr $ has at least one edge. Clearly, for a snapshot array of length $ n $, similarity of snapshots $ s $ is in $ [1,n] $.
\begin{example}
	Consider examples in Fig.~\ref{fig:similarity}.
	\begin{figure}[t] %\vspace*{-0.5cm}
		\begin{center}
			\begin{tabular}[t]{c}\hspace*{-0.3cm}
				\subfigure[{\scriptsize $ s=1 $}]{
					\includegraphics[width=0.5\columnwidth]{fig/example/example_similarity_a.pdf}
				}
				\hspace*{-0.5cm}
				\subfigure[{\scriptsize $ s=4 $}]{
					\includegraphics[width=0.5\columnwidth]{fig/example/example_similarity_b.pdf}
				}
				\\
				\subfigure[{\scriptsize $ s=\frac{5}{3} $}]{
					\includegraphics[width=0.5\columnwidth]{fig/example/example_similarity_c.pdf}
				}
				\hspace*{-0.5cm}
				\subfigure[{\scriptsize $ s=4 $}]{
					\includegraphics[width=0.5\columnwidth]{fig/example/example_similarity_d.pdf}
				}
			\end{tabular}
			\vspace*{-0.5cm}
			\caption{Four snapshot arrays with different similarity of snapshots}
			\vspace*{-0.8cm}
			\label{fig:similarity}
		\end{center}
	\end{figure}
	There are 4 snapshot arrays having the same length of 4 but different similarities of snapshots $ s $. In Fig.~\ref{fig:similarity} (a), $ s=1 $, and we can see that there is no edge shared by any two snapshots, or, snapshots in Fig.~\ref{fig:similarity} (a) are not similar to each other. In Fig.~\ref{fig:similarity} (b) and (d), $ s=4 $, all snapshots share the same edges. In Fig.~\ref{fig:similarity} (c), $ s=\frac{5}{3} $, and there are edges shared by some snapshots.
\end{example}
From the above examples, we can see that with the similarity of snapshots grows, there will be more snapshots in snapshot array which are similar to each other, or, more edges are shared by snapshots.

@@

\begin{definition}[Space Consumption Ratio]
	\label{def:space_consum_ratio}
	Consider an array $ Arr $ holding numeric values or snapshots. If $ Arr $ is a snapshot array, suppose the total number of edges in $ Arr $ is $ E_a $ and the total number of edges in the index is $ E_i $. If $ Arr $ is a numeric array, $ E_a,E_i $ are the total number of numeric values in $ Arr $ and in the index respectively. The space consumption ratio of the index is $ \frac{E_i}{E_a} $.
\end{definition}
\begin{theorem}\label{thm:best_index_space_ratio}
	For two arrays of length $ n $ and starting from 1, snapshot array $ snapArr $ and numeric array $ numArr $, if similarity of snapshots in $ snapArr $ equals $ n $, then the space consumption ratios of the same index built on the two arrays are equal.
\end{theorem}
\comment{
\begin{proof}
	We mentioned that in proof of Theorem~\ref{thm:best_index_efficiency}, the structures of STree built on $ numArr $ and $ snapArr $ are the same. It is the same with the array structure of prefix array and STable. We can turn indexes into sets holding elements like: $ (SumElement,[l,r]) $, and if an index is built on $ numArr $, $ SumElement $ is the aggregation result of numeric values in $ [l,r] $, otherwise the summarized snapshot of snapshots in $ [l,r] $. For each index, suppose we build the index on $ numArr $ and $ snapArr $, named $ numIndex $ and $ snapIndex $. There must be a bijection between elements in $ numIndex $ and $ snapIndex $ that for each $ i $ in $ numIndex $, there is a corresponding $ j $ in $ snapIndex $ that $ i $ and $ j $ have the same time range $ [l,r] $, since the structures of $ numIndex $ and $ snapIndex $ are the same. It is easy to know that the space consumption ratio of $ numIndex $ is $ \frac{|numIndex|}{n} $. Since the similarity of snapshots in $ snapArr $ is $ n $, all snapshots in $ snapArr $ and $ snapIndex $ share the same edges. Suppose the summarized snapshot of snapshots in $ snapArr $ is $ S $, the space consumption ratio of $ snapIndex $ is $ \frac{|snapIndex||S|}{n|S|} $, since $ |snapIndex|=|numIndex| $, so the space consumption ratio of $ snapIndex $ and $ numIndex $ are equal.
\end{proof}
}

@@

\begin{table}[t!]%\vspace*{-0.3cm}
	\scriptsize
	%\small
	\centering
	\caption{\revision{Performance of prefix array and sparse table}} \vspace*{-0.2cm} \label{tab:effi_other_index}
	\begin{tabular}{c c c c c c}
		\toprule
		\makecell[c]{View\\No.}& $ s $ &\makecell[c]{acce-ratio\\preArr} &\makecell[c]{Space ratio\\preArr}&\makecell[c]{acce-ratio\\STable}&\makecell[c]{Space ratio\\STable}\cr %\hline %\hline
		\midrule
		1&53.48&5.37 & 1.51 &12.92 &9.38 \cr
		\midrule
		2&18.16&3.20 & 2.58 &7.87 &14.45 \cr
		\midrule
		3&6.15 &1.76 & 5.76 &5.15 &26.78 \cr
		\midrule
		4&6.07 &1.74 & 5.84 &5.15 &27.04 \cr
		\midrule
		5&4.70 &1.56 & 7.14 &4.84 &31.74 \cr
		\midrule
		6&3.97 &1.45 & 8.33 &4.58 &35.85 \cr
		\midrule
		7&1.12 &0.85 &27.38 &OM & OM \cr
		\bottomrule
	\end{tabular}
	\vspace*{-0.4cm}
\end{table}
\revision{We also implement prefix array (preArr, only supports $ f_e= $ SUM($\ast$)) and sparse table (STable, only supports $ f_e= $ MAX($\ast$) or MIN($\ast$)) to conduct the same queries as a comparison. The results are shown in Table~\ref{tab:effi_other_index}. We can see that the acceleration ratio of prefix array is close to our solution (STree) but with more space consumption in most cases. The performance of prefix array is also influenced by similarity of snapshots, as we analyzed in Section~\ref{sec:effec_of_indexes}. The acceleration ratio of sparse table is much higher than that of prefix array and STree, but consumes much more space. Building sparse table even leads to an out-of-memory on the No. 7 view. Similarly, the performance of sparse table is also influenced by similarity of snapshots. Overall, our index-based method, STree, is the best in these three methods considering both acceleration ratio and space consumption ratio.}
